Reintroduction of resistant frogs facilitates landscape-scale recovery in the presence of a lethal fungal disease

### 2024-04-18 doc/manuscript/PNAS-template-empty.tex
Update PNAS template
Add new figure, text edits, and latex files
Add author contributions and declarations to template

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{}
\authordeclaration{}
\equalauthors{\textsuperscript{1}M.W. contributed equally to this work with A.B.}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: roland.knapp@ucsb.edu}

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{}

>>>>

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{All authors designed research; R.A.K., M.Q.W., A.Q.B., M.B.J., T.C.S., A.P.R., and R.L.G. performed research; M.B.J. contributed new analytic tools; R.A.K., M.Q.W., A.Q.B., A.P.R., and E.B.R. analyzed data; and R.A.K., M.Q.W., A.Q.B., M.B.J., T.C.S., and E.B.R. wrote paper.}
\authordeclaration{This project was supported by grants from the National Park Service (to R.A.K.), Yosemite Conservancy (to R.A.K.), and National Science Foundation (EF-0723563, to C. Briggs; DEB-1557190, to C. Briggs; DEB-2133401, to M.Q.W; and DBI-2120084, to C. Richards-Zawacki). The authors declare no additional competing interests.}
\equalauthors{\textsuperscript{1}M.W. contributed equally to this work with A.B.}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: roland.knapp@ucsb.edu}

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{amphibians | disease | evolution | reintroduction | population recovery}

### 2024-04-18 doc/manuscript/translocation.qmd
Add author contributions and declarations to template

| **Parameter**                                                             | **Value**            | **Source**                                                                        |
|:-------------------------|:------------------|:--------------------------|
| $\sigma_{L_1}$, Yearly survival probability of year-1 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{L_2}$, Yearly survival probability of year-2 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{L_3}$, Yearly survival probability of year-3 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{J_1}$, Yearly survival probability of year-1 juveniles           | Varies yearly        | Varies. Bounds estimated from field data, observations, natural history knowledge |
| $\sigma_{J_2}$, Yearly survival probability of year-2 juveniles           | 0.5                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from CMR studies                                                        |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults        | Varies by population | Estimated from CMR studies                                                        |
| $p_{L_1}$, Probability of a year-1 tadpoles remaining as a tadpoles       | 1                    | Estimated from field data, observations, natural history knowledge                |
| $p_{L_2}$, Probability of a year-2 tadpoles remaining as a tadpoles       | 0.25                 | Estimated from field data, observations, natural history knowledge                |
| $p_{J_1}$, Probability of a year-1 juvenile remaining as a juvenile       | 0.25                 | Estimated from field data, observations, natural history knowledge                |
| $p_F$, Probability of a adult female reproducing in a year                | 0.5                  | Could be as high at 1, based on field observations                                |
| $F$, Number of surviving eggs produced by an adult female                 | 100                  | From observations of captive frogs                                                |

>>>>

| **Parameter**                                                             | **Value**            | **Source**                                                                        |
|:--------------------------------------------------------------------------|:---------------------|:----------------------------------------------------------------------------------|
| $\sigma_{L_1}$, Yearly survival probability of year-1 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{L_2}$, Yearly survival probability of year-2 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{L_3}$, Yearly survival probability of year-3 tadpoles            | 0.7                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{J_1}$, Yearly survival probability of year-1 juveniles           | Varies yearly        | Varies. Bounds estimated from field data, observations, natural history knowledge |
| $\sigma_{J_2}$, Yearly survival probability of year-2 juveniles           | 0.5                  | Estimated from field data, observations, natural history knowledge                |
| $\sigma_{A_R}$, Yearly survival probability of naturally recruited adults | Varies by population | Estimated from CMR studies                                                        |
| $\sigma_{A_T}$, Yearly survival probability of translocated adults        | Varies by population | Estimated from CMR studies                                                        |
| $p_{L_1}$, Probability of a year-1 tadpoles remaining as a tadpoles       | 1                    | Estimated from field data, observations, natural history knowledge                |
| $p_{L_2}$, Probability of a year-2 tadpoles remaining as a tadpoles       | 0.25                 | Estimated from field data, observations, natural history knowledge                |
| $p_{J_1}$, Probability of a year-1 juvenile remaining as a juvenile       | 0.25                 | Estimated from field data, observations, natural history knowledge                |
| $p_F$, Probability of a adult female reproducing in a year                | 0.5                  | Could be as high at 1, based on field observations                                |
| $F$, Number of surviving eggs produced by an adult female                 | 100                  | From observations of captive frogs                                                |
